Paper 1 Analysis

### 2016-02-09 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Added a section on boundary models.

@@

>>>>

\newcommand{\sse}{\mbox{SSE}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Model Discussion}
\label{sec:boundary_model_discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Many other modeling approaches estimate parameters that are close to, 
but not exactly on, a boundary. 
One example is the modeling approach for Portugal wherein
all factors of production are quality-adjusted,
the $(kl)e$ nesting structure is employed, and the CSP is rejected.
The best fitting value of $\delta_1$ is rounds to 
\Sexpr{format(round(naturalCoef(models$PT$adjusted$withE$CES$kle)$delta_1, 3), nsmall = 3)}.
However, if all decimal places determined by the fitting algorithm are reported,
the value of $\delta_1$ is shown to be 
\Sexpr{format(round(naturalCoef(models$PT$adjusted$withE$CES$kle)$delta_1, 20), nsmall = 20)}. 
The fitting algorithm
finds a set of parameters that minimizes the objective function for the fitting algorithm, \sse.
Indeed, the winning, near-boundary model has \sse{} = 
\Sexpr{format(round(sum(resid(models$PT$adjusted$withE$CES$kle)^2), 3), nsmall = 3)},
while the model on the boundary where 
$\delta_1 = 1$ has \sse{} = 
\Sexpr{format(round(sum(resid(attr(models$PT$adjusted$withE$CES$kle, "model.attempts")[[11]])^2), 3), nsmall = 3)}.
